Refining from the BON High-level Specification Language to the VHDL-ASM Hardware Description Language

### 2009-07-27 papers/BON_VHDL/paper.tex
minor changes
minor grammar correction
todo tasks for tomorrow
more text

\section{VHDL-ASM}
\subsection{Hardware description language}

\section{Choice of BON as the modeling tool}
%Brief description and motivation.
The Business Object Notation (BON) is an analysis and design notation 
for object-oriented systems  which emphasizes \emph{seamlessness}, 
\emph{reversibility} and software \emph{contracting}. Let us define 
these principles precisely and point out why the principles are 
important in VHDL-ASM simulation.
%\todo{dragan 25/07/2009 - Figure out relation: Seamlessness and VHDL-ASM}
\begin{itemize}
\item \emph{Seamlessness} is the use of a continuous process 
throughout the software lifecycle.
%\todo{dragan 25/07/2009 - Figure out relation: Reversibility and VHDL-ASM. Why is Reversibility important in VHDL design.}
\item \emph{Reversibility} is the support for both forward and 
backward development process: from analysis to design 
and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up
process. Top-down approach serves for design whereas bottom-up
serves for verification. The possibility of seamlessly translating 
changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various 
models consistent with the code.
\item \emph{Contracting} is the precise definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ).
\end{itemize}

@@

\subsection{Mapping between BON and VHDL-ASM}
%\todo{dragan 25/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\begin{itemize}
\item \Sc: can be represented with high abstract level of the topmost 
entity in a design hierarchy.
\item \Clc: to be described.
\item \Csc: can be identify with the primary unit(\ent) and secondary 
unit (\arch) structure in VHDL-AMS.
The \Csc's name corresponds to the name of the entity in VHDL-AMS.
\item \Ft: The feature section of the \Csc, where the mathematical 
transfer function of the component is entered, holds the same information 
as the \arch section of the VHDL-AMS.
\end{itemize}

@@

\begin{figure}[htp]
\centering
\include{adc-entity}
\caption{An \ent body for a A/D converter.}
\label{figure:adc-entity}
\end{figure}

The \arch body represents description of the internal implementation 
of an \ent including only process statements, which are collections 
of actions to be executed in sequence, or simultaneous statements, 
which describe equations of analogue system behaviour. 
The graphical presentation of \ent is shown in Figure.2
\begin{figure}[htp]
\centering
\include{adc-arch}
\caption{An \arch body for a A/D converter.}
\label{figure:adc-entity}
\end{figure}

>>>>

\section{VHDL-ASM}
VHDL-AMS , as an extension of VHDL, was developed to allow designers 
to represent both analog and digital functionality of a system in 
the same model. Existing hardware description languages, such as VHDL 
and Verilog, support digital systems modeling, while languages such as 
SPICE and its numerous variants support analog systems modeling. 
Integrating these two modeling domains is a significant new capability 
for designers. VHDL-AMS supports the differential and algebraic equations 
(DAEs) where the solution varies continuously with time and, in addition, 
supports both structural composition and behavioural descriptions of 
analogue systems. 
\section{Choice of BON as the modeling tool}
%Brief description and motivation.
The Business Object Notation (BON) is an analysis and design notation 
for object-oriented systems  which emphasizes \emph{seamlessness}, 
\emph{reversibility} and software \emph{contracting}. Let us define 
these principles precisely and point out why the principles are 
important in VHDL-ASM simulation.
%\todo{dragan 25/07/2009 - Figure out relation: Seamlessness and VHDL-ASM}
\begin{itemize}
\item \emph{Seamlessness} is the use of a continuous process 
throughout the software lifecycle.
%\todo{dragan 25/07/2009 - Figure out relation: Reversibility and VHDL-ASM. Why is Reversibility important in VHDL design.}
\item \emph{Reversibility} is the support for both forward and 
backward development process: from analysis to design 
and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up
process. Top-down approach serves for design while bottom-up
serves for verification. The possibility of seamlessly translating 
changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various 
models consistent with the code.
\item \emph{Contracting} is the precise definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ).
\end{itemize}

@@

\subsection{Mapping between BON and VHDL-ASM}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\begin{itemize}
\item \Sc: can be represented with high abstract level of the topmost 
entity in a design hierarchy.
\item \Clc: to be described.
\item \Csc: can be identify with the primary unit(\ent) and secondary 
unit (\arch) structure in VHDL-AMS.
The \Csc's name corresponds to the name of the entity in VHDL-AMS.
\item \Ft: The feature section of the \Csc, where the mathematical 
transfer function of the component is entered, holds the same information 
as the \arch section of the VHDL-AMS.
\end{itemize}

@@

\begin{figure}[htp]
\centering
\include{adc-entity}
\caption{An \ent body for A/D converter.}
\label{figure:adc-entity}
\end{figure}

The \arch body represents description of the internal implementation 
of an \ent including only process statements, which are collections 
of actions to be executed in sequence, or simultaneous statements, 
which describe equations of analogue system behaviour. 
The graphical presentation of \arch is shown in Figure.2
\begin{figure}[htp]
\centering
\include{adc-arch}
\caption{An \arch body for A/D converter.}
\label{figure:adc-entity}
\end{figure} 
%\todo{dragan 27/07/2009 - Start with:1) BON charts and diagrams.}
